%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template for Cover Letter
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Authors:
% David Prieto Melendez <posquit0.bj@gmail.com>
% Lars Richter <mail@ayeks.de>
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%


%-------------------------------------------------------------------------------
% CONFIGURATIONS
%-------------------------------------------------------------------------------
% A4 paper size by default, use 'letterpaper' for US letter
\documentclass[11pt, a4paper]{awesome-cv}

% Configure page margins with geometry
\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}

% Color for highlights
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight
\colorlet{awesome}{awesome-red}
% Uncomment if you would like to specify your own color
% \definecolor{awesome}{HTML}{CA63A8}

% Colors for text
% Uncomment if you would like to specify your own color
% \definecolor{darktext}{HTML}{414141}
% \definecolor{text}{HTML}{333333}
% \definecolor{graytext}{HTML}{5D5D5D}
% \definecolor{lighttext}{HTML}{999999}
% \definecolor{sectiondivider}{HTML}{5D5D5D}

% Set false if you don't want to highlight section with awesome color
\setbool{acvSectionColorHighlight}{true}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}


%-------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%-------------------------------------------------------------------------------
% Available options: circle|rectangle,edge/noedge,left/right
% \photo[circle,noedge,left]{./examples/profile}
\name{David}{Prieto Melendez}
\position{Senior Front-End Web Developer}
% \position{Site Reliability Engineer{\enskip\cdotp\enskip}Software Architect}
\address{Barcelona, 08027, Spain}

\mobile{(+34) 684-153906}
\email{dprietotramites@gmail.com}
%\dateofbirth{January 1st, 1970}
% \homepage{www.posquit0.com}
% \github{posquit0}
\linkedin{david-prieto-928577aa}
% \gitlab{gitlab-id}
% \stackoverflow{SO-id}{SO-name}
% \twitter{@twit}
% \skype{skype-id}
% \reddit{reddit-id}
% \medium{madium-id}
% \kaggle{kaggle-id}
% \hackerrank{hackerrank-id}
% \googlescholar{googlescholar-id}{name-to-display}
%% \firstname and \lastname will be used
% \googlescholar{googlescholar-id}{}
% \extrainfo{extra information}

\quote{``Don't panic."}


%-------------------------------------------------------------------------------
%	LETTER INFORMATION
%	All of the below lines must be filled out
%-------------------------------------------------------------------------------
% The company being applied to
\recipient
  {Fourthline's Recruitment Team}
  {Fourthline\\Barcelona, Barcelona, Spain}
  % {Google Inc.\\1600 Amphitheatre Parkway\\Mountain View, CA 94043}
% The date on the letter, default is the date of compilation
\letterdate{\today}
% The title of the letter
\lettertitle{Job Application for Senior Front-End Web Developer}
% How the letter is opened
\letteropening{Dear Recruitment Team,}
% How the letter is closed
\letterclosing{Sincerely,}
% Any enclosures with the letter
% \letterenclosure[Attached]{Curriculum Vitae}


%-------------------------------------------------------------------------------
\begin{document}

% Print the header with above personal information
% Give optional argument to change alignment(C: center, L: left, R: right)
\makecvheader[R]

% Print the footer with 3 arguments(<left>, <center>, <right>)
% Leave any of these blank if they are not needed
\makecvfooter
  {\today}
  {David Prieto Melendez~~~·~~~Cover Letter}
  {}

% Print the title with above letter information
\makelettertitle

%-------------------------------------------------------------------------------
%	LETTER CONTENT
%-------------------------------------------------------------------------------
\begin{cvletter}

\lettersection{About Me}
I am writing to express my interest in the Senior Frontend Web Developer position at Fourthline, as advertised on LinkedIn. As a highly skilled and experienced developer with a strong passion for front-end development, I am confident that my skills and experience make me a perfect fit for this role.

With over 8 years of experience in front-end development, I have developed a strong understanding and expertise in Angular and Web Components. My experience has allowed me to work on a diverse range of projects, from small webpages to large scale enterprise applications. This has not only sharpened my skills but also helped me develop a strong understanding of different development processes and methodologies.

\lettersection{Why Fourthline?}
What particularly excites me about this position at Fourthline is the company’s focus on cutting-edge technologies and innovation. As a developer, I am constantly seeking opportunities to work with the latest tools and technologies, and I believe that Fourthline offers just that. Your company’s commitment to creating innovative solutions for clients and using the latest technologies aligns perfectly with my own values and career goals.

\lettersection{Why Me?}
In addition to my technical skills, I also possess strong communication and problem-solving abilities. Working in a collaborative environment has taught me the value of effective communication and teamwork. I am confident in my ability to work well with cross-functional teams and contribute to the success of projects.

Moreover, I am also highly adaptable and always eager to learn new skills and technologies. In my last role as a Senior Frontend Developer at NTT Data, I have been responsible for leading the development of multiple projects using Angular and Web Components. I have also been actively involved in the research and implementation of new tools and technologies to improve our development process. This has not only expanded my skills but also helped me stay updated with the latest trends in the industry.

Some of my key accomplishments in my current role include:

- Developed a modern and responsive web application for a client using Angular and Web Components.
- Led the development of a cross-functional team to successfully deliver a complex project within a tight deadline.
- Started and implemented a new Design System for a major company.

I am also highly proficient in CSS preprocessors like SASS, as well as front-end technologies like TypeScrypt, JSX, StencilJS, and Material Design. My experience in working with REST APIs and integrating them with front-end applications makes me confident in my ability to handle any project requirements.

In addition to my technical skills, I am also passionate about giving back to the community and sharing my knowledge with others. I have been actively involved in organizing and speaking at meetups, where I have shared my experience and expertise with other developers. I believe that Fourthline’ focus on social responsibility and community involvement closely aligns with my own values, and I am excited about the opportunity to be a part of such a company.

I am also impressed by Fourthline’ commitment to diversity and inclusivity. As a person who was born and raised overseas, I strongly believe in the importance of creating an inclusive and diverse workplace. I am confident that I will be able to contribute to and thrive in such a culture at Fourthline.

Thank you for considering my application. I am excited about the opportunity to further discuss my qualifications and how I can contribute to the success of your company. I have attached my resume for your review, and I look forward to hearing back from you.

\end{cvletter}


%-------------------------------------------------------------------------------
% Print the signature and enclosures with above letter information
\makeletterclosing

\end{document}
